\documentclass{article}
\title{New Gear}

%
%  This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 Canada License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ca/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.
%

\usepackage{array,supertabular}
\usepackage[british]{babel}
\usepackage[letterpaper,margin=3cm,marginratio=1:1]{geometry}
\usepackage{layouts}
\usepackage{amssymb}

\begin{document}

\pagestyle{empty}
\tabletail{\hline}
\tablelasttail{\hline}

\twocolumn

\subsection*{Sensors}

\subsubsection*{Orientation System}


This sensor functions identically to the orientation system cyberware of page 36, Augmentation.

\subsection*{Vision Enhancements}

\subsubsection*{Optic Light System}

This vision enhancement functions identically to the eye light system cyberware of page 38, Augmentation.

\subsubsection*{Microscopic Vision}

This vision enhancement functions identically to the microscopic vision cyberware of page 38, Augmentation.

\subsection*{Audio Enhancements}

\subsubsection*{Damper}

This audio enhancement functions identically to the damper cyberware of page 341, Shadowrun 20th Anniversary Edition (page 333 Shadowrun 4).

\subsubsection*{Increased Sensitivity}

This audio enhancement functions identically to the increased sensitivity cyberware of page 341, Shadowrun 20th Anniversary Edition (page 333 Shadowrun 4).  If the user is not using a sim module with some form of electrodes or a datajack, the sounds will be transformed into human hearing range sounds.

\subsection*{Military Grade Armour Enhancements}

\subsubsection*{Gecko Tape}

This armour enhancement functions identically to the gecko tape gloves of page 336, Shadowrun 20th Anniversary Edition (page 327 Shadowrun 4).

\subsubsection*{Self Repair}

This armour enhancement functions similarly to the self repair vehicle modification of page 143, Arsenal.  When a piece of armour degrades (as per Armour Degradation, page 44 Arsenal), this enhancement counteracts the effect.  The repair takes one full minute to take effect (during which time the armour functions at the degraded rating).  It has a number of uses equal to the lower of the armours ballistic or impact rating (before any other modification).

The price of the modification is dependant on the lesser of the armours ballistic or impact rating.

Self repair is not compatible with signature masking (below), or gel packs (page 50, Arsenal).

\subsubsection*{Signature Masking}

This armour enhancement functions identically to the signature masking vehicle modification of page 143, Arsenal.  This enhancement does not stack with the thermal damping armour enhancement (signature masking includes thermal damping).

\subsection*{Miscellaneous}

\subsubsection*{Auto Injector}

This item functions identically to the auto injector of page 50, Arsenal, but does not need to be included in armour (taking up capacity).  It is typically strapped to the inside of the users left thigh, with an intravenous needle in the main artery leading directly to the heart.

\subsubsection*{Retinal Contact Molder}

This item functions similarly to the cellular glove molder of page 335, Shadowrun 20th Anniversary Edition (page 324 Shadowrun 4).  

  It produces a pair of contacts which use the wearers own retinal features as much as possible, but overlays them with modifications to mimic that of someone who's retinal pattern is provided.  Due to the difficulty in matching the patterns together and wearing the contacts in the perfect position on the eye to maintain the match the system is very unreliable.  The manufactured contacts function identically to the retinal duplication eyeware of page 340, Shadowrun 20th Anniversary Edition (page 333 Shadowrun 4).

\subsubsection*{Smart Patch}

  These are similar to slap patches (page 80, Arsenal), but do not release their payload until receipt of a command from a timer, wireless link, biomonitor, or other sensor.  Once triggered they are expended, as they hold only one dose of one chemical.  The payload must typically be mixed with DMSO to make it a contact vector drug.

\subsubsection*{SmarTools}

  This cutting edge technology toolkit includes five tools.

  Using technology similar to smart wheels (page 106, Arsenal) it includes a universal power screwdriver, which also doubles as a universal wrench and ratchet set.
  
  A combo clipper, saw (powered), file, knife, pliers, wire cutter and crimper in a butterfly-V handle.
  
  A telescoping combo hammer and crowbar.  A small soldering iron.  
  
  Last but not least is a combo logic analyzer, oscilliscope, spectrum analyzer, digital multimeter which must be monitored by a commlink since it is too small to have it's own interface.

  The electric motors are all virtually silent (-4 to auditory Perception tests), and can be locked to allow for manual manipulation instead.  All are made of lightweight components (reduced weight modification, page 153 Arsenal).  All but the last come with gecko grip (page 152, Arsenal) for easier gripping.  The entire kit comes in a roll up case for easy storage, which can also be worn as a tool belt around the waist, thigh or upper arm.

  This item counts as a build repair kit simultaneously for all of the following skills:  Aeronautics Mechanic, Archery, Armourer, Automatics, Automotive Mechanic, Blades, Clubs, Demolitions, Gunnery, Hardware, Heavy Weapons, Industrial Mechanic, Longarms, Nautical Mechanic, Pistols and Throwing Weapons.

\subsection*{Ammunition}

\subsubsection*{Flash Bang Mortar Rounds}

 This item functions identically to the flash bang grenades of page 324, Shadowrun 20th Anniversary Edition (page 313 Shadowrun 4), albeit a little more powerfully, and using the mortar round rules of page 37 Arsenal. 

\subsubsection*{Subsonic Rounds}

  This functions as a modification to most other ammo types.  Use both the rules for the base ammunition, plus the subsonic round rules of page 35, Arsenal.

\subsection*{Vehicle Modifications}

\subsubsection*{Sensor Upgrade}

\emph{(This item is an optional rule which supersedes and replaces the rules of page 105 and 138 Arsenal.)}

 Vehicle sensor upgrades are limited to +2 above the original rating. Further upgrades require the improved sensor array modification (page 138, Arsenal).  In either case, the maximum sensor rating is 6. Determine the vehicles response and signal per normal rules.

 A vehicle with a vehicle sensor package and the improved sensor array modification may be further upgraded with the missile defense system modification, as per normal.

 The cost for this upgrade is doubled for micro drones.

\onecolumn

\tablehead{
  \hline
  Item & & Capacity & Availability & Cost \\
  \hline \hline
}
\begin{supertabular*}{\columnwidth}{|l!{\extracolsep{\fill}}l|!{\extracolsep{0pt}}c|c|r|}
  \textbf{Sensors} & & & & \\
  Orientation System                          & & [1] &     3  &           250\yen \\ \hline
  \textbf{Vision Enhancements} & & & & \\
  Optic Light System                          & & [1] &    +5  &           150\yen \\
  Microscopic Vision                          & & [2] &    +4  &           300\yen \\ \hline
  \textbf{Audio Enhancements} & & & & \\
  Damper                                      & & [1] &    +4  &           150\yen \\
  Increased Sensitivity                       & & [1] &    +5  &           200\yen \\ \hline
  \textbf{Military Grade Armour Enhancements} & & & & \\
  Gecko Tape                                  & & [2] &     8  &           200\yen \\
  Self Repair                                 & & [4] &    16R & Armour x  500\yen \\
  Signature Masking                           & & Rating & 14F & Rating x  750\yen \\ \hline
  \textbf{Miscellaneous} & & & & \\
  Auto Injector                               & &  -  &     5  &          1500\yen \\
  Retinal Contact Molder (Rating 1-2)         & &  -  &    16F & Rating x 3000\yen \\ 
  Smart Patch                                 & &  -  &     -  &             2\yen \\
  SmarTools                                   & &  -  &    12  &          5000\yen \\
  
\end{supertabular*}

~ \newline

\tablehead{
  \hline
  Item & & Damage & AP & Blast & Availability & Cost \\
  \hline \hline
}
\begin{supertabular*}{\columnwidth}{|l!{\extracolsep{\fill}}l|!{\extracolsep{0pt}}c|c|c|c|r|}
  \textbf{Ammunition} & & & & & & \\
  Flash Bang Mortar                           & &  9S & -3 & 15m & 9R  & 90\yen \\
  Subsonic Round                              & &  -  & +2 &  -  & +8F & +20\yen \\

\end{supertabular*}

~ \newline

\tablehead{
  \hline
  Item & & Slots & Threshold & Tools & Avail & Cost & Special Skill \\
  \hline \hline
}
\begin{supertabular*}{\columnwidth}{|l!{\extracolsep{\fill}}l|!{\extracolsep{0pt}}c|c|c|c|c|c|}
  \textbf{Vehicle Modifications} & & & & & & & \\
  Sensor Upgrade          & & 0 & 8 & Shop & 10 & Rating x 500\yen & Hardware \\

\end{supertabular*}
\end{document}
